---
name: Matthew
surname: Rees
position: "Applied Ecologist"
address: "School of Biosciences, University of Melbourne"
phone: +61 412 560 534
www: matthewreesearch.com
email: "matt.wayne.rees@gmail.com"
twitter: matt_w_rees
github: matt-w-rees
linkedin: matthew-w-rees
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::hyndman:
    keep_tex: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)
library(tidyverse)
library(RefManageR)
library(vitae)
source("functions.R")
```

# About me

I conduct research on predator ecology, invasive animal management and native mammal conservation. To do so, I use quantitative methods which incorporate uncertainty and socio-economic constraints to improve management and decision-making. In particular, my strengths lie in statistical models which estimate animal density, occupancy, spatio-temporal interactions and the integration of different data sources. I'm also passionate about collaborative, open science that incorporates the knowledge and needs of First Nations people. I am currently finishing up my PhD with the [QAECO](https://qaeco.com) lab on the impact of fox control in south-west Victoria, while tackling the occasional, related contracting job.


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD (Conservation Biology)", "2017-present", " University of Melbourne", "Melbourne, Australia",
  "Bachelor of Environmental Science (1st class Honours)", "2013-2016", "Queensland University of Technology", "Brisbane, Australia",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```



# Professional Experience

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2019, 2020, "\\textbf{Ecologist}, Winda-mara Aboriginal Corporation, training Indigenous rangers in fauna monitoring protocols.",
  2020, 2020, "\\textbf{Research assistant}, University of Melbourne, Designing fox density surveys for DELWP knowledge acquisition grant.",
  2018, 2020, "\\textbf{Demonstrator}, University of Melbourne, Conservation Biology, Environmental Risk Assessment subjects.",
) %>%
  arrange(-Start) %>%
  #filter(Start > 2000) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Position) %>%
  baretable()
```


# Publications
### Peer-reviewed
```{r}
library(dplyr)
scholar::get_publications("3vo6a9sAAAAJ&hl") %>% 
 # filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("Rees.bib")

bibliography_entries("Rees.bib")


```

### In peer-review

1.  Davies, H, Tiwi Land Rangers, M Rees, D Stokeld, A Miller, G Gillespie, B Murphy. Variation in feral cat density between two large adjacent islands in Australia’s monsoon tropics. *Biological Invasions*.

### Reports

1.  Rees, M (2020). Monitoring and managing critical weight range mammals in the indigenous protected areas of the world heritage Budj Bim cultural landscape. *A report prepared for the Department of Environment, Land, Water and Planning*.


# Awards

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award, ~Amount,
  2017, "Australian government RTP PhD scholarship", "\\$98K",
  2017, "DELWP PhD top-up scholarship", "\\$15K",
  2016, "CSIRO honours top-up scholarship", "\\$10K",
  2015, "University of Wollongong undergraduate research scholarship", "\\$7.2K"
) %>%
  baretable()
```


# Grants

```{r grants, results='asis'}
grants <- tribble(
  ~Year, ~Award, ~Amount,
  2020, "Hoslworth research endowment", "\\$7.5K",
  2019, "Hoslworth research endowment", "\\$6.75K",
  2018, "Conservation Ecology Centre student scholarship", "\\$5K",
  2017, "Victorian Environmental Assesment Council Bill Borthwick scholarship", "\\$2K",
  2017, "Parks Victoria research partners program", "\\$20K",
  2017, "DELWP research grant", "\\$15K",
) %>%
  baretable()
```


\newpage

# Presentations
* International Statistical Ecology Conference (virtual), June 2020. *Using spatial mark-resight and GAMs to infer predator interactions*.
* Guest lecture, University of Melbourne, Australian Wildlife Biology subject, May 2020, *Invasive mammals in Australia*.
* Ecological Society of Australia, Launceston, November 2019, *Does fox control increase feral cat population density?*
* Wimmera Biodiversity Seminar, Rupanyup, September 2019, *Interactions between invasive predators and threatened native mammals in south-west VIC*.
* Otway Threatened Species Forum, Geelong, August 2019, *Interactions between invasive predators and threatened native mammals in the Otway Ranges*.
* Victorian Biodiversity Conference, Melbourne, February 2019, *Prioritising invasive animal management in the Lake Eyre Basin to benefit both threatened species and agriculture*.
* Ecological Society of Australia, Brisbane, November 2018, *Modelling invasive predator density in mesic forests*.
* Otway Threatened Species Forum, Geelong, August 2018, *How many feral cats are there in the Western Otway Ranges?*
* Mathematics of Biological Systems Symposium, Melbourne, April 2018, *Integrating co-benefits into the cost-effective prioritisation of conservation strategies*.
* Victorian Biodiversity Conference, Melbourne, February 2018, *How many feral cats are there in the Western Otway Ranges?*
* Environmental Institute of Australia & New Zealand conference, Brisbane, August 2017, *Building alliances between the agriculture and conservation sectors*.


# Media
```{r media, results='asis'}
media <- tribble(
  ~Date, ~Format, ~Program, ~Topic,
  "09/12/2019", "Radio interview", "ABC Melbourne", "Invasive predators interactions",
  "08/08/2019", "Radio interview", "3AW", "Invasive predators in south-west VIC",
  "08/08/2019", "Newspaper article (front page)", "Geelong Advertiser", "Invasive predators in south-west VIC",
  "07/08/2019", "Radio interview", "ABC South West Victoria", "Invasive predators in south-west VIC",
  "13/03/2019", "Newspaper article", "Colac Herald", "Feral cat density in the Otway Ranges",
  "11/03/2019", "Radio interview", "ABC Melbourne", "Feral cat density in the Otway Ranges",
  "11/03/2019", "TV interview", "ABC news", "Feral cat density in the Otway Ranges",
  "10/03/2019", "Online news article", "ABC news", "Feral cat density in the Otway Ranges",
  "10/03/2019", "Radio interview", "ABC Ballarat", "Feral cat density in the Otway Ranges",
) %>%
  baretable()
```


# Service
* **Treasurer**, Biosciences Postgraduate Society (2019-2020).
* **Peer-reviewer**, *Wildlife Research* and *Conservation Biology* journals.
* **Award judging panel member**, Ecological Society of Australia (2020).
* **Social media manager**, QAECO lab.


# Referees
* Dr Bronwyn Hradsky, PhD supervisor, bronwyn.hradsky@unimelb.edu.au
* Prof. Brendan Wintle, PhD supervisor, b.wintle@unimelb.edu.au
* Dr Alan Robley, PhD supervisor, alan.robley@delwp.vic.gov.au
* Dr Jack Pascoe, Collaborator, jack@conservationecologycentre.org


