---
name: Matthew
surname: Rees
position: "Applied Ecologist"
address: "School of Biosciences, University of Melbourne"
phone: +61 412 560 534
www: matthewreesearch.com
email: "matt.wayne.rees@gmail.com"
twitter: matt_w_rees
github: matt-w-rees
linkedin: matthew-w-rees
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
source("functions.R")

```


# Profile
I use quantitative methods to improve conservation monitoring, management and decision-making. I specialise in modelling population dynamics and species interactions, tending to focus on predator ecology and invasive species management. My computational toolkit is largely made up of GIS, structured decision-making tools, spatial capture-recapture methods, occupancy models, generalised additive models and integrated population models. I'm also well-versed in field ecology which motivates me to consider what is achievable on-the-ground and fits within socio-economic constraints. More broadly, I'm passionate about transparent, open science which considers the needs and knowledge of Indigenous people. I am currently finishing up my PhD with the [Quantitative and Applied Ecology group](https://qaeco.com) (supervised by Brendan Wintle, Bronwyn Hradsky and Alan Robley) while tackling the occasional, related contracting job.


# Education

```{r education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, 
  "PhD (Conservation Biology)", "2017-present", "University of Melbourne", "Interactions between invasive predators and native prey",
  "Bachelor of Environmental Science (1st class Honours)", "2013-2016", "Queensland University of Technology", "Prioritising invasive animal management in the Lake Eyre Basin, Australia",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```



# Professional Experience

```{r employment}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, 
  "Ecologist", "2019-2020", "Winda-mara Aboriginal Corporation", "Training Indigenous rangers in fauna monitoring protocols",
  "Research assistant", "2020-2020", "University of Melbourne", "Designing fox density field surveys",
  "Demonstrator", "2018-2020", "University of Melbourne", "Conservation Biology, Environmental Risk Assessment subjects",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```



# Publications
### Peer-reviewed
1.  **MW Rees**, J Carwardine, A Reeson and J Firn (2020). Rapidly assessing cobenefits to advance threat‐management alliances. *Conservation Biology*. [https://doi.org/10.1111/cobi.13490](https://doi.org/10.1111/cobi.13490)
2. **MW Rees**, JH Pascoe, BA Wintle, M Le Pla, EK Birnbaum and BA Hradsky (2019). Unexpectedly high densities of feral cats in a rugged temperate forest. *Biological Conservation*, 239, 108287. [https://doi.org/10.1016/j.biocon.2019.108287](https://doi.org/10.1016/j.biocon.2019.108287)

### In peer-review
1.  H Davies, Tiwi Land Rangers, **MW Rees**, D Stokeld, A Miller, G Gillespie and B Murphy. Variation in feral cat density between two large adjacent islands in Australia’s monsoon tropics. *Biological Invasions*.
2. M Le Pla, EK Birnbaum, **MW Rees**, BA Hradsky, AR Weeks, A Van Rooyen and JH Pascoe. Genetic sampling and an activity index indicate contrasting lethal control outcomes. *Journal of Wildlife Management*.

### Reports
1.  **MW Rees** (2020). Monitoring and managing critical weight range mammals in the indigenous protected areas of the world heritage Budj Bim cultural landscape. *A report prepared for the Victorian Government, Department of Environment, Land, Water and Planning*.



# Awards

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award, ~Amount,
  2017, "Victorian Government, Department of Land, Environment, Land, Water and Planning, PhD top-up scholarship", "\\$15K",
  2017, "Australian federal government, RTP PhD scholarship", "\\$98K",
  2016, "Commonwealth Scientific and Industrial Research Organisation, honours top-up scholarship", "\\$10K",
  2015, "University of Wollongong, undergraduate research scholarship", "\\$7.2K"
) %>%
  baretable()
```

\newpage


# Grants

```{r grants, results='asis'}
grants <- tribble(
  ~Year, ~Award, ~Amount,
  2020, "University of Melbourne, School of Biosciences, Jasper Loftus-Hills award", "\\$2.25K",
  2020, "University of Melbourne, School of Biosciences, travel grant ", "\\$2K",
  2020, "Ecological Society of Australia, Hoslworth research endowment", "\\$7.5K",
  2019, "Ecological Society of Australia, Hoslworth research endowment", "\\$6.75K",
  2018, "Conservation Ecology Centre student scholarship", "\\$5K",
  2017, "Victorian Environmental Assesment Council, Bill Borthwick scholarship", "\\$2K",
  2017, "Victorian Government, Parks Victoria research partners program (co-investigator)", "\\$20K",
  2017, "Victorian Government, Department of Land, Environment, Land, Water and Planning research grant", "\\$15K",
) %>%
  baretable()
```




# Presentations
* International Statistical Ecology Conference (virtual), June 2020. *Using spatial mark-resight and GAMs to infer predator interactions*.
* Guest lecture, University of Melbourne, Australian Wildlife Biology, May 2020, *Invasive mammals in Australia*.
* Ecological Society of Australia, Launceston, November 2019, *Does fox control increase feral cat population density?*
* Wimmera Biodiversity Seminar, Rupanyup, September 2019, *Interactions between invasive predators and threatened native mammals in south-west VIC*.
* Otway Threatened Species Forum, Geelong, August 2019, *Interactions between invasive predators and threatened native mammals in the Otway Ranges*.
* Victorian Biodiversity Conference, Melbourne, February 2019, *Prioritising invasive animal management in the Lake Eyre Basin to benefit both threatened species and agriculture*.
* Ecological Society of Australia, Brisbane, November 2018, *Modelling invasive predator density in mesic forests*.
* Otway Threatened Species Forum, Geelong, August 2018, *How many feral cats are there in the Western Otway Ranges?*
* Mathematics of Biological Systems Symposium, Melbourne, April 2018, *Integrating co-benefits into the cost-effective prioritisation of conservation strategies*.
* Victorian Biodiversity Conference, Melbourne, February 2018, *How many feral cats are there in the Western Otway Ranges?*
* Environmental Institute of Australia & New Zealand conference, Brisbane, August 2017, *Building alliances between the agriculture and conservation sectors*.


# Media
```{r media, results='asis'}
media <- tribble(
  ~Date, ~Format, ~Program, ~Topic,
  "09/12/2019", "Radio interview", "ABC Melbourne", "Invasive predators interactions",
  "20/09/2019", "Television segment feature", "TF1 French National News", "Invasive animals in Australia",
  "08/08/2019", "Radio interview", "3AW", "Invasive predators in south-west VIC",
  "08/08/2019", "Newspaper article (front page)", "Geelong Advertiser", "Invasive predators in south-west VIC",
  "07/08/2019", "Radio interview", "ABC South West Victoria", "Invasive predators in south-west VIC",
  "13/03/2019", "Newspaper article", "Colac Herald", "Feral cat density in the Otway Ranges",
  "11/03/2019", "Radio interview", "ABC Melbourne", "Feral cat density in the Otway Ranges",
  "11/03/2019", "Live TV interview", "ABC news", "Feral cat density in the Otway Ranges",
  "10/03/2019", "Online news article", "ABC news", "Feral cat density in the Otway Ranges",
  "10/03/2019", "Radio interview", "ABC Ballarat", "Feral cat density in the Otway Ranges",
) %>%
  baretable()
```


# Service
* **Treasurer**, Biosciences Postgraduate Society (2019-2020).
* **Peer-reviewer**, *Wildlife Research*, *Conservation Biology* and *Austral Ecology* scientific journals.
* **Award judging panel member**, Ecological Society of Australia (2020).
* **Social media manager**, QAECO lab twitter account (2019-present).


# Referees
* Prof. Brendan Wintle, PhD supervisor, b.wintle@unimelb.edu.au
* Dr Bronwyn Hradsky, PhD supervisor, bronwyn.hradsky@unimelb.edu.au
* Dr Alan Robley, PhD supervisor, alan.robley@delwp.vic.gov.au
* Dr Jack Pascoe, Collaborator, jack@conservationecologycentre.org

